Title Goes Here

### 2020-04-28 analysis/paper/paper.Rmd
put ###

cv_plot_site_label <- cv_by_site_df_unnest_label %>% 
  select(-data) %>%

@@

corrplot(COR$r, type="upper", order="hclust", 
         p.mat = COR$P, sig.level = 0.01, insig = "blank")

@@

PCA for 3 factors. We don't think we need this for now. 
```{r}
library(plot3D)

scatter3D(pca_col$PC1, pca_col$PC2, pca_col$PC3, bty = "g", pch = 18, col = gg.col(100), 
          main = "PCA", xlab = "PC1",
          ylab = "PC2", zlab = "PC3")

library(plotly)
plot_ly(pca_col, x = ~PC1, y = ~PC2, z = ~PC3, colors = "Dark2", size = I(120)) %>%  add_markers(color = ~phase)

@@

```{r}
#I'm working on how to read oulines and how to use them for anlaysis. We may not use this for the research.
# reading landmarks and outline in tps, code from Morpho package, adjust readallTPS function. 
readalltps = function(file) 
{
    out = list()
    exOut <- FALSE
    noutline <- 0
    input <- readLines(file)
    LM <- grep("LM=", input)
    LMstring <- input[LM]
    nLM <- sapply(LMstring, strsplit, split = "=")
    nLM <- unlist(nLM)
    nLM <- as.integer(nLM[-which(nLM == "LM")])
    nobs <- length(nLM)
    ID <- grep("ID=", input)
    IDstring <- input[ID]
    nID <- sapply(IDstring, function(x) {
        x <- gsub("=", "_", x)
    })
    nID <- gsub(" ", "", unlist(nID))
    out$ID <- nID
    outline <- grep("CURVES=", input)
    if (length(outline) > 0) {
        exOut <- TRUE
        outlinestring <- input[outline]
        noutline <- sapply(outlinestring, strsplit, split = "=")
        noutline <- unlist(noutline)
        noutline <- as.integer(noutline[-which(noutline == "CURVES")])
        LMoutline <- (sapply(outline, function(x) {
            x <- max(which(LM < x))
        }))
    }
    LMdata <- list()
    for (i in 1:nobs) {
        if (nLM[i] > 0) {
            LMdata[[i]] <- as.numeric(unlist(strsplit(unlist(input[c((LM[i] + 
                1):(LM[i] + nLM[i]))]), split = " ")))
            LMdata[[i]] <- matrix(LMdata[[i]], nLM[i], 2, byrow = TRUE)
        }
        else LMdata[[i]] <- NA
    }
    names(LMdata) <- nID
    out$LM <- LMdata
    if (exOut) {
        outlineData <- list()
        for (i in 1:nobs) {
            if (i %in% LMoutline) {
                i1 <- grep(i, LMoutline)
                outlinetmp <- list()
                ptr <- outline[i1] + 1
                j <- 1
                while (j <= noutline[i1]) {
                  tmpnr <- as.integer(unlist(strsplit(input[ptr], 
                    split = "="))[2])
                  outlinetmp[[j]] <- matrix(as.numeric(unlist(strsplit(input[(ptr + 
                    1):(ptr + tmpnr)], split = " "))), tmpnr, 
                    2, byrow = TRUE)
                  ptr <- ptr + tmpnr + 1
                  j <- j + 1
                }
                outlineData[[i]] <- outlinetmp
            }
            else outlineData[[i]] <- NA
        }
        names(outlineData) <- nID
        out$outlines <- outlineData
    }
    cat(paste("Read", nobs, "datasets with", sum(noutline), "outlines\n"))
    return(out)
}

#try to read all data(landmarks and outlines) from one file
lm_trial <- readalltps(here("analysis/data/raw_data/A_BG_2.tps"))

#read all files from raw_data
tps_files <- list.files(here("analysis/data/raw_data"), full.names = TRUE)
lm_landmarks <- map(tps_files, readalltps)
names(lm_landmarks) <- list.files(here("analysis/data/raw_data"))

lm_landmarks = c()
for (i in 1:length(files)) {
  filename <- paste(datadir, files[i], sep = "")
  print(filename)
  landmarks <- readalltps(filename)
 lm_landmarks <- c(lm_landmarks, landmarks)
}

>>>>

cv_plot_site_label <- cv_by_site_df_unnest_label %>%
                select(-data)

@@

@@

@@

```{r}
#I'm working on how to read oulines and how to use them for anlaysis. We may not use this for the research.
# reading landmarks and outline in tps, code from Morpho package, adjust readallTPS function.

#readalltps = function(file) 
{
   # out = list()
   # exOut <- FALSE
  # noutline <- 0
  # input <- readLines(file)
   # LM <- grep("LM=", input)
  # LMstring <- input[LM]
   # nLM <- sapply(LMstring, strsplit, split = "=")
  #  nLM <- unlist(nLM)
   # nLM <- as.integer(nLM[-which(nLM == "LM")])
  #  nobs <- length(nLM)
   # ID <- grep("ID=", input)
  #  IDstring <- input[ID]
   # nID <- sapply(IDstring, function(x) {
   #     x <- gsub("=", "_", x)
  #  })
   # nID <- gsub(" ", "", unlist(nID))
  #  out$ID <- nID
   # outline <- grep("CURVES=", input)
  #  if (length(outline) > 0) {
   #     exOut <- TRUE
    #    outlinestring <- input[outline]
     #   noutline <- sapply(outlinestring, strsplit, split = "=")
      #  noutline <- unlist(noutline)
      #  noutline <- as.integer(noutline[-which(noutline == "CURVES")])
    #    LMoutline <- (sapply(outline, function(x) {
   #         x <- max(which(LM < x))  })) }
 #   LMdata <- list()
  #  for (i in 1:nobs) {
  #      if (nLM[i] > 0) {
   #         LMdata[[i]] <- as.numeric(unlist(strsplit(unlist(input[c((LM[i] + 
      #          1):(LM[i] + nLM[i]))]), split = " ")))
       #     LMdata[[i]] <- matrix(LMdata[[i]], nLM[i], 2, byrow = TRUE)
        }
   #     else LMdata[[i]] <- NA }
   # names(LMdata) <- nID
  #  out$LM <- LMdata
   # if (exOut) {
    #    outlineData <- list()
     #   for (i in 1:nobs) {
      #      if (i %in% LMoutline) {
       #         i1 <- grep(i, LMoutline)
        #        outlinetmp <- list()
         #       ptr <- outline[i1] + 1
          #      j <- 1
           #     while (j <= noutline[i1]) {
            #      tmpnr <- as.integer(unlist(strsplit(input[ptr], 
        #            split = "="))[2])
         #         outlinetmp[[j]] <- matrix(as.numeric(unlist(strsplit(input[(ptr + 
         #           1):(ptr + tmpnr)], split = " "))), tmpnr, 
          #          2, byrow = TRUE)
           #       ptr <- ptr + tmpnr + 1
            #      j <- j + 1  }
             #   outlineData[[i]] <- outlinetmp  }
          #  else outlineData[[i]] <- NA }
       # names(outlineData) <- nID
      #  out$outlines <- outlineData }
 #   cat(paste("Read", nobs, "datasets with", sum(noutline), "outlines\n"))
#    return(out)}

#try to read all data(landmarks and outlines) from one file
# lm_trial <- readalltps(here("analysis/data/raw_data/A_BG_2.tps"))

#read all files from raw_data
# tps_files <- list.files(here("analysis/data/raw_data"), full.names = TRUE)
# lm_landmarks <- map(tps_files, readalltps)
# names(lm_landmarks) <- list.files(here("analysis/data/raw_data"))

#lm_landmarks = c()
#for (i in 1:length(files)) {
#  filename <- paste(datadir, files[i], sep = "")
 # print(filename)
#  landmarks <- readalltps(filename)
# lm_landmarks <- c(lm_landmarks, landmarks)}
